THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY.

### 2016-10-04 DishReflectometry/Paper1_v3.tex
Final reading up to section 6

    %i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
    In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
    resulting in the delay spectrum:
    \begin{eqnarray}
    \tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
    \label{eq3}
    \end{eqnarray}
    % XXX rethink how to express this equation (not correct about integrated over all sky)
    % XXX define tau_g
    The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
    It was then shown that the this delay-transformed visibility related to the power spectrum of redshifted
    21 cm emission as
    \begin{equation}
      P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
    \label{eq4}
    \end{equation}
    where
    \begin{equation}
      k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
      k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
     \label{eq5}
    \end{equation}
    The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
    $f_{21}$:rest frame frequency of the 21~cm radiation.\\
    $f$: observation frequency.\\
    $z$: cosmological redshift corresponding to the frequency of observation.\\
     $\Delta B$: bandwidth centered at the observation frequency.\\
     $k_\textrm{B}$: Boltzmann constant.\\
     $D\equiv D(z)$ comoving distance along the line of sight\\
     $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
    $E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
    \indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.

    \indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay
    $\tau$, corresponding to the given baseline length, the redshifted 21 cm power
    spectrum could be estimated from the delay spectrum of the visibility measured
    by an interferometer. The sky delay spectrum from any direction $\thhat$ is
    convolved with the delay spectrum of the instrument and would be located at the
    delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
     in the delay domain. The maximum geometric delay possible for a given baseline would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$, when the phase centre is halfway in between the two antennas. %The phase center is elsewhere defined as being at the center of one of the antennas.
     Hence, the sky contribution from any direction would be confined within
    $-\tau_{g}<\tau<\tau_{g}$. Due to the chromaticity of the sky signal as well as
    the instrument response, the delay spectrum of the sky spills over into delays
    with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12].
    The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power
    spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the
    sky delay spectrum $P_{sky}(\tau)$.Therefore, in the spill over region
    $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground,
    with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay
    spectrum could be detectable.

@@

    The Hydrogen Epoch of Reionization Array consists of parabolic dishes which
    provide increased collecting area per array element compared to its predecessor
    experiment PAPER. Plane waves incident on a parabolic dish are focussed at the
    feed which is kept at the focal plane of the dish.  The mismatch between the
    impedance of free space and the feed and transmission line results in a partial
    coupling of the sky signal into the feed while the rest is reflected off the
    feed.  The reflected signal illuminates the dish and most of it is reflected
    back into the space.  However, a part of it reflects back and forth several
    times in between the feed and the vertex of the dish which is shadowed by the
    feed.  Such reflections generate multiple copies of the incident sky signal of
    reduced strength at various delay and phase and thus produces spurious
    correlations in the visibilities of interferometric data.  Identical spurious
    visibilities could be resulted due to reflections internal to the system
    causing delay space distortion. Therefore, it is necessary to measure and
    understand the instrument delay spectrum in order to qualify the system for the
    measurement of 21cm power spectrum.  In this section we compute the visibility
    of a two element interferometer accounting for the additional reflections of
    the sky signal in between the feed and the dish vertex and the corresponding
    effects on the delay spectrum in detail. We assume two antennas with identical
    geometry and electrical parameters i.e,
    $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.

@@

    \section{\textbf{Reflectometry measurements}}

    Reflectometry is a method of determining the multiple reflection of any signal within a system. 
    If applied to a radio telescope such as a parabolic dish, this could determine the extent to which 
    sky signal is reflected back and forth between the reflector and the feed ~\citep{2015arXiv150205862P}.
    Reflectometry measurements are carried out at the HERA element prototype in
    Green Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument
    response of the feed and dish assembly and characterise the performance.  HERA
    element consists off a $14\,m$ diameter parabolic reflector and a
    crossed-dipole pair as a feed. The cross dipole antenna pair is identical to
    the feed of the PAPER antenna which is suspended at the focal plane of the dish
    with the support of three vertical poles. HERA elements are closely spaced with
    centre to centre distance between two dishes are equal to the dish diameter.
    Therefore, to reduce the coupling between the adjacent dishes, the crossed
    dipole feed along with the back plane is encased in a cylindrical cage. The
    feed is raised and lowered by a three-pulley system mounted on the three poles.
    The focal height of the dish is $5m$.  The detail geometry and electromagnetic
    design of of the feed is presented in deBoer et al 2016. \\

@@

    Comparing equations \ref{eq13} and \ref{eq2}, the cross power generated by
    $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual
    correlation between multiply reflected voltages represented by the second and
    the third term of the right hand side of equation \ref{eq13}. In the ideal
    case, $\Gamma_{f}=0$, in which case equation \ref{eq13} results in equation
    \ref{eq2}. The Fourier transform of this visibility spectrum along the
    frequency axis results in the delay spectrum.  In the delay domain,
    visibilities contributed to by any two voltage components from two antennas
    with no mutual delay will be located at the delay $\tau = 0$ whereas any two
    voltage components from two antennas having a mutual delay of $n\Delta \tau$
    will be centred at $n\Delta \tau$. These will broaden the width of the delay
    spectrum, which ultimately interferes with the 21cm power spectrum detection.

@@

    During observation, each HERA element is connected to an active balun similar
    to the ones used in the PAPER antenna which provides greater than 10dB return
    loss of power at the feed output. These baluns are currently under further design 
    improvements aiming at 10 to 20dB
    better impedance match between the feed and the backend.
    Measurements presented here is done using a vector network analyzer for
    which the active balun has been replaced by a passive balun.Given the antenna
    impedance and the 50 Ohm transmission line the measurements are done using the
    passive balun with a 4:1 impedance ratio. This measurements are conservative
    estimate  for both $\Gamma_{f}$ and $s_{11}$.\\ While measuring the return loss
    of the dish-feed assembly, the signal transmitted by the VNA is reflected first
    off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq9}. This
    essentially represents a mismatch in between the feed and the 50 Ohm
    transmission line. In delay domain, this appears at the zero delay bin. The
    zero delay response is identical whether or not the feed is suspended on the
    dish. Therefore, we measure this response by measuring the feed return loss
    alone while the feed is kept on the ground facing the sky. This results in feed
    return loss alone including the surrounding cage structure but excluding the
    dish response. While $\Gamma_{f}$ fraction of incident voltage is reflected off
    the feed, $1+\Gamma_{f}$ fraction of the voltage is transmitted. In receiving
    mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected
    back in to the space while $1+\Gamma_{f}$ voltage enters the feed. In receiving
    mode, in delay domain, this appears at the zero delay bin.  The using the
    return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement
    $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq11} and
    the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.

@@

    Measurement equations shows the effects of multiple reflections of the sky
    signal between the feed and the dish. Any other reflections off the feed
    structure and/or any other part of the dish-feed assembly would appear at
    arbitrary delays. The estimated delay spectrum of the instrument is
    collectively contributed by all the reflections. Delay spectrum estimated from
    the return loss measurement of the feed alone,  provides the lowest limit of
    the delay spectrum of the instrument considering there is no multiple
    reflections in between the feed and the dish.  From figure
    \ref{ds_feed_on_dish_trans}, at lower delays, the reflections are dominated by
    the feed structure. Therefore, the delay spectrum in both the cases follow each
    other. Since the distance between the feed and the dish is 5 m, the roundtrip
    delay between the dish and the feed as about $30~ns$. Hence, the dish
    reflection is expected to manifest themselves at an integral multiple of
    $30~ns$. The diameter of the feed cavity is $172~cm$  that results in signal
    reflections every integral multiple of $\approx2.86~ns$. The combined effect of
    feed and the dish dominates the delay spectrum up to $\> 50nS$ after which the
    dish reflections starts to dominate and the two delay spectrum deviates from
    each other. With some manipulation of the equation \ref{eq10}, we can estimate
    the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in
    figure \ref{dish_delay_spectrum}.

@@

    Another effect that spills over of the smooth foreground power at higher delays
    is the multiple reflection of the received signal between the feed output and
    the input of the analog backend and correlators. In our measurements, the feed
    output is connected to the VNA via a 50 feet long LMR 400 cable. This length
    corresponds to a delay of $\approx 120~nS$ for the signals traveling through
    the cable. The delay spectrum of both feed and feed-dish assembly shows an
    enhanced feature around this delay indicating a reflection from the VNA input. We
    measure the VNA input reflections by disconnecting the feed and connecting an
    open load at the feed input of the cable. The measured return loss is shown in
    figure \ref{fig:open_RL}. Since the electromagnetic wave traveling through
    a transmission line undergoes a $100\%$ reflections from an open ended
    transmission line, we compute the combined effect of the VNA input return loss
    along with the cable resistive loss from this measurement as shown in figure
    \ref{fig:open_RL}. This results an important system design criterion for HERA.
    The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across
    the measurement band. This is consistent with the matched provided by the
    commercially available RF connectors that are commonly used. This manifests
    itself in a peak in the delay spectrum which is $50~dB$ above the measurement
    noise floor. The delays at which this effect becomes dominant depends on the
    length of the cable. Since our measurement plane is at the open end of the cable
    first reflection appears at zero delay while the second one appears around 120~ns. 
    Peak amplitude of the consecutive reflection is reduced by $22~dB$. Third and 
    consecutive reflections are buried in the noise floor of this measurement.Due to 
    finite return loss at the input of the backends,
    this effect will be present in all the observations and thus would impact the
    instrument delay spectrum. However, its effect could be reduced below the level
    where the foreground  achieving a return loss at the backend input is greater
    than at least $-30~dB$.

@@

  \subsection{Comparison with simulations:}
  \begin{figure}{H}
  \centering
  \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/simulation_comparison2.png}
  \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
   \label{fig:sim_em}
   \end{figure}
 \subsubsection{Electromagnetic simulation:}  
 Performance of the HERA feed and the dish-feed assembly has been simulated by
    the em solver "High Frequency Structural Simulator(HFSS)" using the finite
    element method.  The simulated and measured return loss of the feed, both
    magnitude and phase are shown in the upper panel of figure
    \ref{RL_mag_dish}. Bottom panel of figure \ref{RL_mag_dish} shows the measured return loss when
    feed is suspended at the focal plane of the parabolic dish which is at $5m$
    from the dish vertex. The measured return loss is much more complex than what
    is found from simulation. 
    While the simulated return loss of the feed structure shows
    two resonant peaks around 120 and $160~MHz$, the feed resonance occur at
    slightly higher frequencies. Notable are the difference in the shape of the
    resonant peaks. While the simulated response shows very wide resonant peaks, as
    expected from these dipole structures, the measured return loss has
    a narrow peak at its low frequency resonance. The dominant term in the expression of  return loss of the HERA element in
    receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. Hence the low frequency peak dominates the overall shape of the delay spectrum in figure
    \ref{fig:sim_em}.\\

>>>>

    %i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as, 
    In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
    resulting in the delay spectrum:
    \begin{eqnarray}
    %\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	  
     \tilde V(\vec b, \tau) & = & \beam(\vec b,\tau)*I_\sky(\vec b,\tau)
                           %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
    \label{eq3}
    \end{eqnarray}
    % XXX rethink how to express this equation (not correct about integrated over all sky)
    % XXX define tau_g
    The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. Qualitatively, 
    delay spectrum of the visibility results from the convolution of the delay spectrum of the instrument with the instrument delay response. It is, therefore, important to determine the instrument delay response in order to determine sky delay response at a particular delay. by de-convolving the delay transformed visibility by the instrument response.

   The delay-transformed visibility is related to the power spectrum of redshifted
    21 cm emission by the relation, 
    \begin{equation}
     %P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
     %\end{equation}
     %\begin{equation}
 P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 {X^{2}Y \over \Omega \Delta B}
    \label{eq4}
    \end{equation}
    where
    \begin{equation}
      k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
      k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
     \label{eq5}
    \end{equation}
    where, \\
    \begin{itemize}
    \item
     $f_{21}$:rest frame frequency of the 21~cm radiation.\\
     \item
    $f$: observation frequency.\\
    \item
    $z$: cosmological redshift corresponding to the frequency of observation.\\
    \item
     $\Delta B$: bandwidth centered at the observation frequency.\\
     \item
     $k_\textrm{B}$: Boltzmann constant.\\
     \item
     $D\equiv D(z)$ comoving distance along the line of sight\\
     \item
     $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
     \item
    $E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
    \item
    X, Y are cosmological scalers that relates the angular dependence with spectral frequency to corresponding comoving distance.
    \end{itemize}
   % \indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
    %\indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay
    %$\tau$, corresponding to the given baseline length, the redshifted 21 cm power
    %spectrum could be estimated from the delay spectrum of the visibility measured
    %by an interferometer. 
    %The sky delay spectrum from any direction $\thhat$ is
    %convolved with the delay spectrum of the instrument and would be located at the
    %delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
     %in the delay domain. The maximum geometric delay possible for a given baseline would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$, when the phase centre is halfway in between the two antennas. %The phase center is elsewhere defined as being at the center of one of the antennas.
     %Hence, the sky contribution from any direction would be confined within
    %$-\tau_{g}<\tau<\tau_{g}$. Due to the chromaticity of the sky signal as well as
    %the instrument response, the delay spectrum of the sky spills over into delays
    %with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12].
    %The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power
    %spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the
    %sky delay spectrum $P_{sky}(\tau)$.Therefore, in the spill over region
   % $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground,
    %with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay
    %spectrum could be detectable.

@@

    HERA consists of parabolic dishes which
    provide increased collecting area per array element compared to its predecessor
    experiment PAPER. Plane waves incident on a parabolic dish are focussed at the
    feed which is kept at the focal plane of the dish.  The mismatch between the
    impedance of free space and the feed and transmission line results in a partial
    coupling of the sky signal into the feed while the rest is reflected off the
    feed.  The reflected signal illuminates the dish and most of it is reflected
    back into the space.  However, a part of it reflects back and forth several
    times in between the feed and the vertex of the dish which is shadowed by the
    feed.  Such reflections generate multiple copies of the incident sky signal of
    reduced strength at various delay and phase and thus produces spurious
    correlations in the visibilities of interferometric data.  Identical spurious
    visibilities could be resulted due to reflections internal to the system
    causing delay space distortion. Therefore, it is necessary to measure and
    understand the instrument delay spectrum in order to qualify the system for the
    measurement of 21cm power spectrum.  In this section we compute the visibility
    of a two element interferometer accounting for the additional reflections of
    the sky signal in between the feed and the dish vertex and the corresponding
    effects on the delay spectrum in detail. We assume two antennas with identical
    geometry and electrical parameters i.e,
    $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.

@@

    \section{\textbf{Reflectometry}}

    Reflectometry is a method of determining the multiple reflection of any signal within 
    a system in either time or frequency domain. If applied to a radio telescope such as
     a parabolic dish, this could determine the extent to which 
    sky signal is reflected back and forth between the reflector and the feed ~\citep{2015arXiv150205862P}.
    Frequency domain reflectometry measurements are carried out at the HERA element prototype in
    Green Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument
    response of the feed and dish assembly and characterise the performance.  HERA
    element consists off a $14\,m$ diameter parabolic reflector and a
    crossed-dipole pair as a feed. The cross dipole antenna pair is identical to
    the feed of the PAPER antenna which is suspended at the focal plane of the dish
    with the support of three vertical poles. HERA elements are closely spaced with
    centre to centre distance between two dishes are equal to the dish diameter.
    Therefore, to reduce the coupling between the adjacent dishes, the crossed
    dipole feed along with the back plane is encased in a cylindrical cage. The
    feed is raised and lowered by a three-pulley system mounted on the three poles.
    The focal height of the dish is $5m$.  The detail geometry and electromagnetic
    design of of the feed is presented in deBoer et al 2016. \\

@@

    Comparing equations \ref{eq13} and \ref{eq2}, the cross power generated by
    $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual
    correlation between multiply reflected voltages represented by the second and
    the third term of the right hand side of equation \ref{eq13}. In the ideal
    case, $\Gamma_{f}=0$, in which case equation \ref{eq13} results in equation
    \ref{eq2}. The Fourier transform of this visibility spectrum along the
    frequency axis results in the delay spectrum.  In the delay domain,
    visibilities contributed to by any two voltage components from two antennas
    with no mutual delay will be located at the delay $\tau = 0$ whereas any two
    voltage components from two antennas having a mutual delay of $n\Delta \tau$
    will be centred at $n\Delta \tau$. These will result in leakage of the foreground 
    at delays where EoR power spectrum could be measured.
   % spectrum, which ultimately interferes with the 21cm power spectrum detection.

@@

    During observation, each HERA element is connected to an active balun similar
    to the ones used in the PAPER antenna which provides greater than 10dB return
    loss of power at the feed output. These baluns are currently under further design 
    improvements aiming at 10 to 20dB
    better impedance match between the feed and the backend.
    Measurements presented here is done using a vector network analyzer for
    which the active balun has been replaced by a passive balun.Given the antenna
    impedance and the 50 Ohm transmission line, the measurements are done using the
    passive balun with a 4:1 impedance ratio. These measurements are conservative
    estimate  for both $\Gamma_{f}$ and $s_{11}$.\\ While measuring the return loss
    of the dish-feed assembly, the signal transmitted by the VNA is reflected first
    from the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq9}. This
    essentially represents a mismatch in between the feed and the 50 Ohm
    transmission line. In delay domain, this appears at the zero delay bin. The
    zero delay response is identical whether or not the feed is suspended on the
    dish. Therefore, we measure this response by measuring the feed return loss
    alone while the feed is kept on the ground facing the sky. This results in feed
    return loss alone including the surrounding cage structure but excluding the
    dish response. While $\Gamma_{f}$ fraction of incident voltage is reflected off
    the feed, $1+\Gamma_{f}$ fraction of the voltage is transmitted. In receiving
    mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected
    back in to the space while $1+\Gamma_{f}$ voltage enters the feed. In receiving
    mode, in delay domain, this appears at the zero delay bin.  The using the
    return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement
    $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq11} and
    the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.

@@

    Measurement equations shows the effects of multiple reflections of the sky
    signal between the feed and the dish. Any other reflections off the feed
    structure and/or any other part of the dish-feed assembly would appear at
    arbitrary delays. The estimated delay spectrum of the instrument is
    collectively contributed by all the reflections. Delay spectrum estimated from
    the return loss measurement of the feed alone,  provides the lowest limit of
    the delay spectrum of the instrument considering there is no multiple
    reflections in between the feed and the dish.  From figure
    \ref{ds_feed_on_dish_trans}, at lower delays, the reflections are dominated by
    the feed structure. Therefore, the delay spectrum in both the cases follow each
    other. Since the distance between the feed and the dish is 5 m, the roundtrip
    delay between the dish and the feed as about $30~ns$. Hence, the dish
    reflection is expected to manifest themselves at an integral multiple of
    $30~ns$. The diameter of the feed cavity is $172~cm$  that results in signal
    reflections every integral multiple of $\approx2.86~ns$. The combined effect of
    feed and the dish dominates the delay spectrum up to $\> 50nS$ after which the
    dish reflections starts to dominate and the two delay spectrum deviates from
    each other. 
    %With some manipulation of the equation \ref{eq10}, we can estimate
    %the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in
    %figure \ref{dish_delay_spectrum}.

@@

    Another effect that spills over of the smooth foreground power at higher delays
    is the multiple reflection of the received signal between the feed output and
    the input of the analog backend and correlators. In our measurements, the feed
    output is connected to the VNA via a 50 feet long LMR 400 cable. This length
    corresponds to a delay of $\approx 120~nS$ for the signals traveling through
    the cable. The delay spectrum of both feed and feed-dish assembly shows an
    enhanced feature around this delay indicating a reflection from the VNA input. We
    measure the VNA input reflections by disconnecting the feed and connecting an
    open load at the feed input of the cable. The measured return loss is shown in
    figure \ref{fig:open_RL}. Since the electromagnetic wave traveling through
    a transmission line undergoes a $100\%$ reflections from an open ended
    transmission line, we compute the combined effect of the VNA input return loss
    along with the cable resistive loss from this measurement as shown in figure
    \ref{fig:open_RL}. This results an important system design criterion for HERA.
    The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across
    the measurement band. This is consistent with the specification provided by the
    commercially available RF connectors that are commonly used. This manifests
    itself in a peak in the delay spectrum which is $50~dB$ above the measurement
    noise floor. The delays at which this effect becomes dominant depends on the
    length of the cable. Since our measurement plane is at the open end of the cable
    first reflection appears at zero delay while the second one appears around 120~ns. 
    Peak amplitude of the consecutive reflection is reduced by $22~dB$. Third and 
    consecutive reflections are buried in the noise floor of this measurement.Due to 
    finite return loss at the input of the backends,
    this effect will be present in all the observations and thus would impact the
    instrument delay spectrum. However, its effect could be reduced below the level
    where the foreground  achieving a return loss at the backend input is greater
    than at least $-30~dB$. Moreover, if cable length are sufficiently increased
    without the loss of signal, these reflections could be made to occur at delays
    which are not of interest for EoR measurements.

@@

  \subsection{Comparison with simulations}
  \begin{figure}{H}
  \centering
  \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/simulation_comparison2.png}
  \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
   \label{fig:sim_em}
   \end{figure}
 \subsubsection{Electromagnetic simulation:}  
 Performance of the HERA feed and the dish-feed assembly has been simulated by
    the em solver "High Frequency Structural Simulator(HFSS)" using the finite
    element method.  The simulated and measured return loss of the feed, both
    magnitude and phase are shown in the upper panel of figure
    \ref{RL_mag_dish}. Bottom panel of figure \ref{RL_mag_dish} shows the measured return loss when
    feed is suspended at the focal plane of the parabolic dish which is at $5m$
    from the dish vertex. The measured return loss is much more complex than what
    is found from simulation. 
    While the simulated return loss of the feed structure shows
    two resonant peaks around 120 and $160~MHz$, the feed resonance occur at
    slightly higher frequencies. Notable are the difference in the shape of the
    resonant peaks. While the simulated response shows very wide resonant peaks, as
    expected from these dipole structures, the measured return loss has
    a narrow peak at its low frequency resonance. The dominant term in the expression of  return loss of the HERA element in
    receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. Hence the feed return loss, especially the shape of the low frequency resonant peak dominates the overall shape of the delay spectrum in figure
    \ref{fig:sim_em}.\\
